### 2022-01-18 manuscript/submission.tex
revisao geophysics correcoes valeria

The first and second rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
the true upward-continued total-field anomalies at a height of $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
are produced by the same three synthetic bodies: two prisms and one sphere with 
constant total-magnetization vector having inclination, declination and intensity of 
$35.26^{\circ}$, $45^{\circ}$, and $3.4641$ A/m, respectively. 
The simulated main geomagnetic field has inclination and declination of $35.26^{\circ}$ and $45^{\circ}$,
respectively.

@@

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the results obtained
with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
This figure shows that the data residuals 
obtained by the classical method (upper panel) produced an acceptable data fit, having mean 
$0.4070$ nT and standard deviation $0.3899$ nT. 
%Using our method, the data residuals (middle panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
%standard deviation $0.7462$ nT produced a worse data fitting.
%The convergence of our method (lower panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
%similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
%increasing without achieving an invariance. Hence, the convergence is not achieved. 
%
%\textbf{Alternative text} $\rightarrow$
%
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $1.5129$ nT and 
standard deviation $1.8526$ nT also produced a good data fitting.
The convergence of our method (lower panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
to a constant value close to iteration $50$. Note that this good result was obtained by 
using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
%
%$\leftarrow$ \textbf{Alternative text}

@@

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the differences
between the true upward-continued total-field anomalies (third row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
anomalies (not shown). We conveniently denote these differences as continuation
residuals.

%% Classical and our method

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows that the continuation residuals 
obtained by using the classical method (upper row) and our method (middle row) are 
similar to each other in most of the tests.
The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface 
(Figures \ref{fig:synthetic_data_comparison_v2}e and 
\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
requirement of regular grids or a flat observation surface, demanded by our method.
Note that the maximum absolute value of the continuation residuals produced by using our 
method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
are $\approx 2$ times greater than those produced by the classical method 
(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
%Besides, they are generally concentrated at the boundaries of the study area.

In contrast, the continuation residuals obtained by using the 
classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
Note that, similar to our method, the maximum absolute values of the continuation residuals 
obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
However, the values are significantly higher.

%% Reduction to pole
Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows the differences
between the true reduced to pole total-field anomalies (fourth row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted reduced to pole total-field 
anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.

%% Classical and our method

Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures and \ref{fig:synthetic_zrtp_residuals_comparison_v2}c \ref{fig:synthetic_zrtp_residuals_comparison_v2}e). The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
As in the the continuation test, they are generally concentrated at the boundaries of the study area.

@@

Important to note that the reduction to pole, using the equivalent layer, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).

We also call attention to the following aspects:
In applying the classical method, our method, or the classical Fourier approach, we do not expand 
the data by using a padding scheme.
The data residuals (upper and middle rows in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}), 
the continuation and reduction to pole residuals (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) are shown without removing edge effects. 
The computational time required by our method is much lower than that required by the classical method
and has the same order of magnitude of that required by the classical Fourier approach.
However, the classical Fourier approach shows upward-continued and reduced to pole data with strong border effects if no padding scheme is applied to expand the data.

@@

Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
horizontal plane located at $5, \,000$ m using the estimated equivalent layer obtained by applying our
method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
without visible errors or border effects. 
Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
horizontal plane located at $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies.

@@

\plot{synthetic_data_comparison_v2}{width=9cm}{
	{Synthetic tests: the simulated airborne magnetic surveys  - 
		The first row shows the grids of observation points and the undulating observation surfaces that simulate the airborne magnetic surveys. 
		The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row. 
		The third row shows the  noise-free total-field anomalies produced by the synthetic sources 
		at $z = -1,300$ m (the true upward-continued total-field anomalies).
		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys as follows: 
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_data_comparison_v2}
}

\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
	{Synthetic tests: the data residuals and convergence - 
		The first row shows the data residuals using the classical method.
		The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_residuals_convergence_comparison_v2}
}

\plot{synthetic_upward_residuals_comparison_v2}{width=10cm}{
	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the upward-continued total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m 
		(third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and
		the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_upward_residuals_comparison_v2}
}

\plot{synthetic_zrtp_residuals_comparison_v2}{width=10cm}{
	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the reduced to pole total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $-900$ m height. 
		(b) A irregular grid with uncertainty of $20\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(c) A irregular grid with uncertainty of $30\%$  in the $x-$ and $y-$coordinates and a flat observation surface at $-900$ m height. 
		(d) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $5\%$. 
		(e) A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainty of $10\%$. 
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_zrtp_residuals_comparison_v2}
}

@@

\plot{carajas_upward_comparison}{width=13cm}{
	{(a) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using our method.
		(b) Upward continuation transformation of real data of Carajás Province, Brazil at $5, \,000$ m using the classical Fourier method.}
	\label{fig:carajas_upward_comparison}
}

>>>>

The first and second rows in Figure \ref{fig:synthetic_data_comparison_v2} show, respectively, 
the simulated flight patterns and noise-corrupted total-field anomalies of the airborne magnetic 
surveys used in our tests. The third row in Figure \ref{fig:synthetic_data_comparison_v2} shows 
the true upward-continued total-field anomalies at $z = -1, \, 300$ m. The fourth row in Figure \ref{fig:synthetic_data_comparison_v2} shows the true reduced to pole total-field anomalies.
All magnetic data (second and lower rows in Figure \ref{fig:synthetic_data_comparison_v2}) 
are produced by the same three synthetic bodies: two prisms and one sphere with 
constant total-magnetization vector having inclination, declination and intensity of 
$35.26^{\circ}$, $45^{\circ}$, and $3.4641$ A/m, respectively. 
The simulated main geomagnetic field has inclination and declination of $35.26^{\circ}$ and $45^{\circ}$,
respectively.

@@

Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c shows the results obtained
with the irregular data grid perturbed by using $30\%$ of the regular grid spacing.
The data residuals 
obtained by the classical method (upper panel in Figure \ref{fig:synthetic_residuals_convergence_comparison_v2}c) produced an acceptable data fit, having mean 
$0.4070$ nT and standard deviation $0.3899$ nT. 
%Using our method, the data residuals (middle panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $0.9788$ nT and 
%standard deviation $0.7462$ nT produced a worse data fitting.
%The convergence of our method (lower panel in Figure 
%\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
%similarly to the previous results, the Euclidean norm of the residuals decreases; however it starts
%increasing without achieving an invariance. Hence, the convergence is not achieved. 
%
%\textbf{Alternative text} $\rightarrow$
%
Using our method, the data residuals (middle panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) with mean $1.5129$ nT and 
standard deviation $1.8526$ nT also produced a good data fitting.
The convergence of our method (lower panel in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}c) shows that, 
similarly to the previous results, the Euclidean norm of the residuals decreases; converging 
to a constant value close to iteration $50$. Note that this good result was obtained by 
using a very perturbed data grid (upper panel in Figure \ref{fig:synthetic_data_comparison_v2}c).
%
%$\leftarrow$ \textbf{Alternative text}

@@

Figure \ref{fig:synthetic_upward_residuals_comparison_v2} shows the continuation residuals defined as the differences
between the true upward-continued total-field anomalies (third row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted upward-continued total-field 
anomalies (not shown). We conveniently denote these differences as continuation
residuals.
%% Classical and our method 
The continuation residuals 
obtained by using the classical method (upper row) and our method (middle row) are 
similar to each other in most of the tests.
The exceptions are the synthetic test with data over irregular grid (Figures \ref{fig:synthetic_data_comparison_v2}c and \ref{fig:synthetic_residuals_convergence_comparison_v2}c) and over an undulating surface 
(Figures \ref{fig:synthetic_data_comparison_v2}e and 
\ref{fig:synthetic_residuals_convergence_comparison_v2}e), which greatly violates the 
requirement of regular grids or a flat observation surface, demanded by our method.
Note that the maximum absolute value of the continuation residuals produced by using our 
method (middle panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e) 
are $\approx 2$ times greater than those produced by the classical method 
(upper panel in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}e).
%Besides, they are generally concentrated at the boundaries of the study area.

%%  Fourier 
In contrast, the continuation residuals obtained by using the 
classical Fourier approach (lower row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2})
are, in most of the tests, approximately $2$ times greater than those produced by the classical method 
(upper row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and $1.5$ times greater than
those produced by our method (middle row in Figure \ref{fig:synthetic_upward_residuals_comparison_v2}).
Note that, similar to our method, the maximum absolute values of the continuation residuals 
obtained by using the classical Fourier approach are located at the boundaries of the simulated area.
However, the values are significantly higher.

%% Reduction to pole
Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows the differences
between the true reduced to pole total-field anomalies (fourth row in Figure
\ref{fig:synthetic_data_comparison_v2}) and the predicted reduced to pole total-field 
anomalies (not shown). The true reduced to pole total-field anomalies are generated by using only induced magnetization, with $I_{0} = 90^{\circ}$ and $D_{0} = 0^{\circ}$.
%% Classical and our method 
Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2} shows that the reduced to pole residuals 
obtained by using the classical method (upper row) and our method (middle row) have differences when high irregular grids or non flat surfaces are used (Figures \ref{fig:synthetic_zrtp_residuals_comparison_v2}c and \ref{fig:synthetic_zrtp_residuals_comparison_v2}e). The absolute values of the reduced to pole residuals are almost $\approx 2$ times greater than those of classical method when the $10\%$ standard deviation was used (upper and middle panels in Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}e, respectively).
As in the the continuation test, they are generally concentrated at the boundaries of the study area.

@@

Important to note that the reduction to pole, either using the equivalent layer or the Fourier approach, has the requirement of a previously knowledge of the sources magnetization directions (equation \ref{eq:u_hat}) to obtain a correct source parameter estimative, otherwise, only non-phase dependent processing can be used (upward continuation for example).

We also call attention to the following aspects:
In applying the classical method, our method, or the classical Fourier approach, we do not expand 
the data by using a padding scheme.
The data residuals (upper and middle rows in Figure 
\ref{fig:synthetic_residuals_convergence_comparison_v2}), 
the continuation (Figure \ref{fig:synthetic_upward_residuals_comparison_v2}) and reduction to pole residuals (Figure \ref{fig:synthetic_zrtp_residuals_comparison_v2}) are shown without removing edge effects. 
The computational time required by our method is much lower than that required by the classical method
and has the same order of magnitude of that required by the classical Fourier approach.
However, the classical Fourier approach shows upward-continued and reduced to pole data with strong border effects if no padding scheme is applied to expand the data.

@@

Finally, Figure \ref{fig:carajas_upward_comparison}a shows the upward-continued magnetic data to a
horizontal plane located at an altitude of $5, \,000$ m using the estimated equivalent layer obtained by applying our
method to the decimated irregular grid. This process took $\approx 2.64$ seconds, showing good results 
without visible errors or border effects. 
Figure \ref{fig:carajas_upward_comparison}b shows the upward-continued magnetic data to a
horizontal plane located at an altitude of $5, \,000$ m using the classical Fourier filtering method to the decimated irregular grid.
This process took $\approx 0.5$ seconds. Altough, no border effect could be observed, this result showed unexpected high values instead of the expected attenuation of the anomalies. We stress that we did not use a padding scheme to expand the data.

@@

\plot{synthetic_data_comparison_v2}{width=9cm}{
	{Synthetic tests: the simulated airborne magnetic surveys  - 
		The first row shows the grids of observation points and the undulating observation surfaces that simulate the airborne magnetic surveys. 
		The second row shows the noise-corrupted total-field anomalies produced by the synthetic sources and calculated on the simulated airborne magnetic survey shown in the first row. 
		The third row shows the  noise-free total-field anomalies produced by the synthetic sources 
		at $z = -1,300$ m (the true upward-continued total-field anomalies).
		The fourth row shows the noise-free total-field anomalies produced by the synthetic sources at inclination $I_{0} = 90\circ$ (the true reduced to pole total-field anomalies).
		The results shown in these last three rows were obtained by using the simulated airborne magnetic surveys as follows:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_data_comparison_v2}
}

\plot{synthetic_residuals_convergence_comparison_v2}{width=\textwidth}{
	{Synthetic tests: the data residuals and convergence - 
		The first row shows the data residuals using the classical method.
		The second and third rows show, respectively, the data residuals and the convergence curves using the convolutional equivalent layer (our method).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_residuals_convergence_comparison_v2}
}

\plot{synthetic_upward_residuals_comparison_v2}{width=\textwidth}{
	{Synthetic tests: the data residuals of the upward-continued total-field anomalies (third row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the upward-continued total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at $z = -1,300$ m 
		(third  row in Figure \ref{fig:synthetic_data_comparison_v2}) and
		the predicted total-field anomaly at $z = -1,300$ m  obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_upward_residuals_comparison_v2}
}

\plot{synthetic_zrtp_residuals_comparison_v2}{width=\textwidth}{
	{Synthetic tests: the data residuals of the reduced to pole total-field anomalies (fourth row 
		in Figure \ref{fig:synthetic_data_comparison_v2}).
		The data residuals of the reduced to pole total-field anomalies are defined as the difference between 
		the noise-free total-field anomaly produced by the synthetic sources at the pole (fourth  row in Figure \ref{fig:synthetic_data_comparison_v2}) and the predicted total-field anomaly obtained by using three methods:
		the classical method (first row); the convolutional equivalent layer (second row); and 
		the classic approach in the Fourier domain (third row).
		The results shown in these three rows were obtained by using the simulated airborne magnetic surveys shown in Figure \ref{fig:synthetic_data_comparison_v2}, i.e.:
		(a) A regular grid of $100 \times 50$ observation points in the $x-$ and $y-$directions and a flat observation surface at $z= -900$ m. 
		An irregular grid with uncertainties of (b) $20\%$ and (c) $30\%$   in the $x-$ and $y-$coordinates and a flat observation surface at $z= - 900$ m . 
		A regular grid  of $100 \times 50$ observation points in the $x-$ and $y-$coordinates and an undulating observation surface with uncertainties of (d) $5\%$ and  (e) $10\%$.
		The black lines represent the horizontal projection of the sources
		.}
	\label{fig:synthetic_zrtp_residuals_comparison_v2}
}

@@

\plot{carajas_upward_comparison}{width=13cm}{
	{Upward continuations of real data of Carajás Province, Brazil at altitude of 5,000 m by using:
		(a) the convolutional equivalent layer (our method) and (b) the classical Fourier method.}
	\label{fig:carajas_upward_comparison}
}
